---
title: "Exploratory Figure Generation"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Does following our recommendation save money?

First let's load in the data

```{r}
load("../Pre_Generated_Output_Data/House_case_objectives/Hypothetical_houses.RData")
```

The first question is how our recommendations differ from those of FEMA.
We can plot a histogram of the difference:

```{r}
additional_heightening <- opt_height - fema_height
hist(additional_heightening, freq = FALSE, ylab = "", yaxt="n", main = "Our Guidelines Change Recommendations", xlab = "Optimal Height Minus FEMA Guidelines (ft)")
abline(v=0, lwd=3, lty=3, col="blue")
```

The next question is whether this leads to savings.
We can plot a histogram of the savings, as a percentage of house value.

```{r}
savings <- fema_totcost - opt_totcost
savings_pct <- savings / SOWs[, 2] # second col of SOW is value
hist(savings_pct, freq = FALSE, ylab = "", yaxt="n", main = "Our Guidelines Save Money", xlab="Expected Savings From Optimal Strategy vs FEMA Guidelines (% of Home Value)")
abline(v=0, lwd=3, lty=3, col="blue")
```

This suggests that most homeowners will save between 0 and 10 percent of the value of their home, but that some will save much more and a few will lose money.
**Maggie's results differed, did I make a coding mistake?**

Last we can compare results

```{r}
plot(
  additional_heightening, savings_pct,
  main = "One Dot Equals One House",
  ylab = "Expected Savings (% of Home Value)",
  xlab = "Optimal Height Minus FEMA Guidelines (ft)"
)
abline(v=0, lwd=3, lty=3, col="blue")
abline(h=0, lwd=3, lty=3, col="blue")
```

This shows that sometimes FEMA recommends very large increases that don't make any sense.
If we assume that common sense will save the homeowners who are told by FEMA that they should elevate 5 feet when this doesn't make sense, we can zoom in on the right portion of this graph:

```{r}
to_plot <- additional_heightening >= -4
plot(
  additional_heightening[to_plot], savings_pct[to_plot],
  main = "One Dot Equals One House",
  ylab = "Expected Savings (% of Home Value)",
  xlab = "Optimal Height Minus FEMA Guidelines (ft)"
)
abline(v=0, lwd=3, lty=3, col="blue")
abline(h=0, lwd=3, lty=3, col="blue")
```

This shows that sometimes FEMA suggests to raise the house by a few feet when it's not needed, and that homeowners can save a lot of money by electing to not elevate in these cases (left portion of graph) and that being proactive and elevating a few feet beyond FEMA guidelines can save homeowners up to about three percent of the value of their home.